First Exclusive Measurement of Deeply Virtual Compton Scattering off $^4$He: Toward the 3D Tomography of Nuclei

### 2017-05-11 eg6-letters/coherent/dvcs_he4_prl.tex
Comments from SS

%
\date{\today}
\begin{abstract}
We report on the first measurement of the beam-spin asymmetry in the 
exclusive process of coherent deeply virtual 
Compton scattering off a nucleus for $A>1$. The experiment used the 6 GeV 
electron beam from the CEBAF accelerator at Jefferson Lab incident on a 
$^4$He gas target in front of the CEBAF Large Acceptance Spectrometer 
(CLAS). While the electron was detected by CLAS and the gamma by a dedicated
electromagnetic calorimeter at forward angles, a specially designed radial 
time projection chamber was used to detect the recoiling $^4$He
nuclei and to ensure the exclusivity of the process. The measured beam-spin 
asymmetries are larger than those observed on the free proton in the same kinematic 
domain. Since $^4$He is a spin-zero target, we were able to extract, in a 
model-independent way, the real and imaginary parts of its unique 
Compton form factor, $\cal H_A$. This pioneering measurement of coherent deeply virtual 
Compton scattering on the $^4$He nucleus, with a fully exclusive final state 
via nuclear recoil tagging, leads the way toward 3D imaging of the partonic 
structure of nuclei.
\end{abstract}
\pacs{Valid PACS appear here}

@@

In Fig.~\ref{fig:alu90}, the $Q^2$, $x_{B}$, and $t$-dependencies of the fitted 
$A_{LU}$ at $\phi$~=~90$^{\circ}$ are shown. The $x_{B}$ and $t$-dependencies 
are compared to theoretical calculations by S.~Liuti and K.~Taneja 
\cite{simonetta_2}. The model accounts for the effect on the quark distribution 
of the virtuality (off-shellness) of the nucleon. The calculations are at slightly 
different kinematics than our data but still allow drawing some conclusions. The 
calculations appear to have smaller asymmetries than observed. 
The difference may arise from the theoretical uncertainty in the determination 
of the crossing point where the parton nuclear distribution becomes larger than the 
nucleon one, and reverses the sign of the nuclear effect.

>>>>

%
\date{\today}
\begin{abstract}
We report on the first measurement of the beam-spin asymmetry in the 
exclusive process of coherent deeply virtual 
Compton scattering off a nucleus. The experiment used the 6 GeV 
electron beam from the CEBAF accelerator at Jefferson Lab incident on a 
$^4$He gas target in front of the CEBAF Large Acceptance Spectrometer 
(CLAS). While the electron was detected by CLAS and the gamma by a dedicated
electromagnetic calorimeter at forward angles, a specially designed radial 
time projection chamber was used to detect the recoiling $^4$He
nuclei and to ensure the exclusivity of the process. The measured beam-spin 
asymmetries are larger than those observed on the free proton in the same kinematic 
domain. Since $^4$He is a spin-zero target, we were able to extract, in a 
model-independent way, the real and imaginary parts of its unique 
Compton form factor, $\cal H_A$. This pioneering measurement of coherent deeply virtual 
Compton scattering on the $^4$He nucleus, with a fully exclusive final state 
via nuclear recoil tagging, leads the way toward 3D imaging of the partonic 
structure of nuclei.
\end{abstract}
\pacs{Valid PACS appear here}

@@

In Fig.~\ref{fig:alu90}, the $Q^2$, $x_{B}$, and $t$-dependencies of the fitted 
$A_{LU}$ at $\phi$~=~90$^{\circ}$ are shown. The $x_{B}$ and $t$-dependencies 
are compared to theoretical calculations by S.~Liuti and K.~Taneja 
\cite{simonetta_2}. The model accounts for the effect of the nucleon virtuality 
(off-shellness) on the quark distribution. The calculations are at slightly 
different kinematics than our data but still allow drawing some conclusions. The 
calculations appear to have smaller asymmetries than observed. 
The difference may arise from the theoretical uncertainty in the determination 
of the crossing point where the parton nuclear distribution becomes larger than the 
nucleon one, and reverses the sign of the nuclear effect.
